---
title: "Rcapstone"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rcapstone}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package contains functions to clean and visualise earthquake data.

## Load Library
```{r, message=FALSE}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(leaflet)
library(Rcapstone)
```

## Import Dataset
The raw dataset is obtained from National Geophysical Data Center / World Data Service (NGDC/WDS): Significant Earthquake Database. National Geophysical Data Center, NOAA. Click here [doi:10.7289/V5TD9V7K](http://dx.doi.org/10.7289/V5TD9V7K)

For convenience, the data has been preloaded into `./inst/extdata/dataset.txt`.

```{r, message=FALSE}
raw_data <- system.file("extdata", "dataset.txt", 
                        package = "Rcapstone")
```

## Clean Data
This create a cleaned data for earthquakes since 01 Jan 1900, excluding data points with missing magnitude or intensity.
```{r, message=FALSE}
cleaned_data <- eq_clean_data(raw_data)
cleaned_data <- eq_location_clean(cleaned_data)
head(cleaned_data, 5)
```

## Create Timeline Plot
```{r, fig.height=4, fig.width=5}
ggplot(data = cleaned_data, 
       aes(x = DATE, country = COUNTRY, label = LOCATION, magnitude = MAGNITUDE)) +
  geom_timeline(ctry = "MEXICO", xmin = dmy("01/01/2000"), xmax = dmy("01/01/2018")) +
  geom_timeline_label(n_max = 2, ctry = "MEXICO", 
                      xmin = dmy("01/01/2000"), xmax = dmy("01/01/2018")) +
  theme_classic()
```

## Create Map Plot
```{r, fig.height=4, fig.width=5}
cleaned_data %>% 
  filter(COUNTRY == "MEXICO" & year(DATE) >= 2000) %>% 
  mutate(popup_text = eq_create_label(.)) %>% 
  eq_map(annot_col = "popup_text")
```
